Diffantom: a whole-brain diffusion MRI phantom derived from a real dataset

### 2015-08-12 paper/main.tex
fix #33

\section*{Disclosure/Conflict-of-Interest Statement}

@@

\begin{figure}[h!]
\begin{center}
\includestandalone[width=\linewidth]{figure01}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure1} Figure \arabic{figure}. }%
{\textbf{Generation of \emph{diffantoms}:} First, a microstructural model is generated as described
  in the \nameref{sec:data_generation} subsection.
Please note the piece-wise linear function of the color scale to enable visibility of small volume fractions.
This microstructural model is fed into a simulation block that generates the final \gls*{dmri} dataset
  as described in the second block.
}
\end{figure}

>>>>

\section*{Disclosure}

@@

\begin{figure}[h!]
\begin{center}
\includestandalone[width=\linewidth]{figure01}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:figure1} Figure \arabic{figure}. }{%
\textbf{A. Microstructural model of \emph{Diffantom}}.
The phantom is simulated from an underlying microstructural model specified with the
  following volume-fraction maps: three hindered-diffusion compartments $\{T_1, T_2, T_3\}$,
  one free-diffusion compartment $T_4$ corresponding to the \gls*{csf},
  three restricted-diffusion compartments $\{F_i\}$, and three vectorial maps
  associated with the local fiber directions $\{\mathbf{V}_i\}$.
Please note the piece-wise linear function of the color scale to enable visibility of small volume fractions.
\textbf{B. Workflow to generate \emph{diffantoms}}.
The pipeline to generate phantoms from any \gls*{hcp} dataset is presented in the lower box.
Once the microstructural model shown in the upper box has been prepared as described in \nameref{sec:data_model},
  the local orientations are computed and fed into \emph{Phantomas} to finally generate the signal.
}
\end{figure}
